---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

[![Travis-CI Build Status](https://travis-ci.org/jknowles/maintainr.svg?branch=master)](https://travis-ci.org/jknowles/maintainr)

# maintainr

Stupid simple R package installation tracking.

## Introduction

`maintainr` is a simple package with a simple goal -- to produce an export of 
installed packages on an R installation and read in that export from another 
R installation. Currently, `maintainr` provides the ability to backup this list 
of installed packages and their version to a Dropbox account via the excellent 
`rdrop2` package. 

This package is not meant to be a way to standardize installs for production systems. 
Instead, it is to solve two specific problems I have with using R: 

1. Upgrading my R installation seamlessly on Windows
2. Keeping track of installed packages across multiple machines used for analysis 
(work, home, virtual test environment)

## Installation

To install `maintainr`: 

```{r eval=FALSE}
library(devtools)
install_github("jknowles/maintainr")
library(maintainr)
```

## Backup Packages

```{r eval=TRUE}
library(maintainr)
myPkgs <- pkg_list()
knitr::kable(head(myPkgs))
```

I want to keep this in sync across two machines so I store the list of 
installed packages to a central location.

```{r eval=FALSE}
pkg_backup(cloudProvider = "dropbox", dest = "/zzz")

```

This stores a csv file in the specified location.

Now I can sync or restore. 

```{r eval=FALSE}
# Path for dropbox is from the root of the Dropbox directory
out <- pkg_restore(filename="zzz/RPackageBackup_2016-12-08.csv", 
                   cloudProvider = "dropbox", install = FALSE)
head(out)

pkgList <- readCloud(filename="zzz/RPackageBackup_2016-12-08.csv", 
                   provider = "dropbox")

sync_pkgs(pkgList = pkgList, keep_all = TRUE)

out <- pkg_restore(filename="zzz/RPackageBackup_2016-12-08.csv", 
                   cloudProvider = "dropbox", install = FALSE)
head(out)

```

## Backup R Configuration Files

Coming soon...

## To Do

- Write a package vignette
- Unit tests?
- Sync R Profile Site
- Make Renviron point to library independently
- Make setting the R library path independent
- Set R Profile Site configuration

### Links that help

[Upgrading R on Windows](http://www.r-statistics.com/wp-content/uploads/2010/04/upgrading-R-on-windows.r.txt)

[Install New R on Windows](http://stackoverflow.com/questions/1401904/painless-way-to-install-a-new-version-of-r-on-windows)

### Contributing

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
